Proposed Solution

### 2017-01-24 CAV17/secs/motiv.tex
fxing learner
cav17: motiv

\section{Motivating Examples}
\label{sec-motiv}

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    MISSING ENTRY ERROR: Expected "extension=pgsal.so"
    in the same file: "extension=curl.so"
    w/ confidence ...
\end{lstlisting}

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
  FINE GRAINED ERROR:
  Expected "max_connections" * "sort_buffer_size"
               > "key_buffer_size"
\end{lstlisting}

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
TYPE ERROR: Expected a PType {string = 2, path = 0, int = 37, bool = 7, size = 0} 
  for "slow-query-log"
\end{lstlisting}

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
ORDERING ERROR: Expected "innodb_data_home_dir[mysqld]" BEFORE
"innodb_data_file_path[mysqld]" 
  w/ confidence {tru = 17, fls = 1}
\end{lstlisting}

>>>>

\section{Motivating Examples}
\label{sec:motiv}

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
    MISSING ENTRY ERROR: Expected "extension=pgsal.so"
    in the same file: "extension=curl.so"
\end{lstlisting}

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
FINE GRAINED ERROR: Expected 
  "max_connections" * "sort_buffer_size" >= "key_buffer_size"
\end{lstlisting}

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
TYPE ERROR: Expected an integer type for "slow-query-log"
\end{lstlisting}

@@

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
ORDERING ERROR: Expected "innodb_data_home_dir[mysqld]" BEFORE
  "innodb_data_file_path[mysqld]" 
\end{lstlisting}
